Algorithm Selection for Graph Algorithms

### 2015-12-11 portfolio/as-graphs.Rnw
more algsel variants, tweaked plots, everything in milliseconds

<<echo=FALSE, message=FALSE, warning=FALSE>>=
opts_chunk$set(comment=NA, fig.width='\\textwidth', fig.height=5, fig.pos='!ht')
library(llama)
library(BBmisc)
library(xtable)
library(plyr)
library(aslib)
library(tidyr)

@@

tabs = by(ldf$data, ldf$data$family, function(x) as.data.frame.matrix(t(sapply(x[,ldf$performance], mean))))
tab = rbind.fill(tabs)
tab$family = rownames(tab)
tab = tab[,order(names(tab))]
print(xtable(tab, digits = 3, caption = "Mean performance by family."), booktabs = TRUE, include.rownames = FALSE)

@@

tabs = by(ldf$data, ldf$data$family, function(x) as.data.frame.matrix(t(sapply(x[,ldf$performance], median))))
tab = rbind.fill(tabs)
tab$family = rownames(tab)
tab = tab[,order(names(tab))]
print(xtable(tab, digits = 3, caption = "Median performance by family."), booktabs = TRUE, include.rownames = FALSE)

@@

res = summarizeAlgoPerf(asscenario)
print(xtable(res, digits = 6, display = c("s", "d", "d", rep("g", 8))), booktabs = TRUE)
@

@@

<<echo=FALSE, results='asis'>>=
res = summarizeAlgoRunstatus(asscenario)
print(xtable(res, digits = 3), booktabs = TRUE)
@

@@

tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
print(xtable(tab, digits = 3, caption = "Preliminary algorithm selection results."), booktabs = TRUE, include.rownames = FALSE)
@

@@

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@

@@

tabs = by(ldf3$data, ldf3$data$family, function(x) as.data.frame.matrix(t(sapply(x[,ldf3$performance], mean))))
tab = rbind.fill(tabs)
tab$family = rownames(tab)
tab = tab[,order(names(tab))]
print(xtable(tab, digits = 3, caption = "Mean performance by family."), booktabs = TRUE, include.rownames = FALSE)

@@

tabs = by(ldf3$data, ldf3$data$family, function(x) as.data.frame.matrix(t(sapply(x[,ldf3$performance], median))))
tab = rbind.fill(tabs)
tab$family = rownames(tab)
tab = tab[,order(names(tab))]
print(xtable(tab, digits = 3, caption = "Median performance by family."), booktabs = TRUE, include.rownames = FALSE)

@@

tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
print(xtable(tab, digits = 3, caption = "Preliminary algorithm selection results with presolved instances removed."), booktabs = TRUE, include.rownames = FALSE)
@

@@

tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
print(xtable(tab, digits = 3, caption = "Preliminary algorithm selection results with presolved instances removed (evaluated on all instances)."), booktabs = TRUE, include.rownames = FALSE)
@

@@

perfs = subset(ldf3$data, TRUE, c("instance_id", ldf3$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@

@@

<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
# presolver
ldf2 = ldf3
presolvetime = 0.05
ldf2$data = subset(ldf3$data, ldf3$data$vf2 > presolvetime)
ldf2$best = subset(ldf3$best, ldf3$data$vf2 > presolvetime)
ldf2$train = NULL
ldf2$test = NULL
ldf2 = cvFolds(ldf2)
timesss = subset(timess, timess$instance %in% ldf2$data$instance_id)
ldf2$data$family = factor(timesss[order(timesss$instance, as.character(ldf2$data$instance_id)), 'family'])
ldf2$extra = "family"

@@

tabs = by(ldf2$data, ldf2$data$family, function(x) as.data.frame.matrix(t(sapply(x[,ldf2$performance], mean))))
tab = rbind.fill(tabs)
tab$family = rownames(tab)
tab = tab[,order(names(tab))]
print(xtable(tab, digits = 3, caption = "Mean performance by family."), booktabs = TRUE, include.rownames = FALSE)

@@

tabs = by(ldf2$data, ldf2$data$family, function(x) as.data.frame.matrix(t(sapply(x[,ldf2$performance], median))))
tab = rbind.fill(tabs)
tab$family = rownames(tab)
tab = tab[,order(names(tab))]
print(xtable(tab, digits = 3, caption = "Median performance by family."), booktabs = TRUE, include.rownames = FALSE)

@@

tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
print(xtable(tab, digits = 3, caption = "Preliminary algorithm selection results with presolver."), booktabs = TRUE, include.rownames = FALSE)
@

@@

tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
print(xtable(tab, digits = 3, caption = "Preliminary algorithm selection results with presolver (evaluated on all instances)."), booktabs = TRUE, include.rownames = FALSE)
@

@@

perfs = subset(ldf2$data, TRUE, c("instance_id", ldf2$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@

@@

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@

>>>>

<<echo=FALSE, message=FALSE, warning=FALSE>>=
opts_chunk$set(comment=NA, fig.width='\\textwidth', fig.height=5, fig.pos='!ht')
library(llama)
library(BBmisc)
library(xtable)
library(plyr)
library(aslib)
library(tidyr)
library(ggthemes)
library(scales)

@@

tabs = by(ldf$data, ldf$data$family, function(x) as.data.frame.matrix(t(sapply(x[,ldf$performance], mean))))
tab = rbind.fill(tabs)
tab$family = rownames(tab)
tab = tab[,order(names(tab))]
print(xtable(tab, digits = 0, caption = "Mean performance by family."), booktabs = TRUE, include.rownames = FALSE)

@@

tabs = by(ldf$data, ldf$data$family, function(x) as.data.frame.matrix(t(sapply(x[,ldf$performance], median))))
tab = rbind.fill(tabs)
tab$family = rownames(tab)
tab = tab[,order(names(tab))]
print(xtable(tab, digits = 0, caption = "Median performance by family."), booktabs = TRUE, include.rownames = FALSE)

@@

res = summarizeAlgoPerf(asscenario)
print(xtable(res, digits = 0, display = c("s", "d", "d", rep("g", 8))), booktabs = TRUE)
@

@@

<<echo=FALSE, results='asis'>>=
res = summarizeAlgoRunstatus(asscenario)
print(xtable(res, digits = 0), booktabs = TRUE)
@

@@

tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
print(xtable(tab, digits = 0, caption = "Preliminary algorithm selection results."), booktabs = TRUE, include.rownames = FALSE)
@

@@

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(0,1)) +
    ylab("fraction of instances solved") + xlab("time [ms]") +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='sans', base_size = 12) +
    theme(legend.justification=c(1,0), legend.position=c(1,0.1), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))
@

@@

tabs = by(ldf3$data, ldf3$data$family, function(x) as.data.frame.matrix(t(sapply(x[,ldf3$performance], mean))))
tab = rbind.fill(tabs)
tab$family = rownames(tab)
tab = tab[,order(names(tab))]
print(xtable(tab, digits = 0, caption = "Mean performance by family."), booktabs = TRUE, include.rownames = FALSE)

@@

tabs = by(ldf3$data, ldf3$data$family, function(x) as.data.frame.matrix(t(sapply(x[,ldf3$performance], median))))
tab = rbind.fill(tabs)
tab$family = rownames(tab)
tab = tab[,order(names(tab))]
print(xtable(tab, digits = 0, caption = "Median performance by family."), booktabs = TRUE, include.rownames = FALSE)

@@

tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
print(xtable(tab, digits = 0, caption = "Preliminary algorithm selection results with presolved instances removed."), booktabs = TRUE, include.rownames = FALSE)
@

@@

tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
print(xtable(tab, digits = 0, caption = "Preliminary algorithm selection results with presolved instances removed (evaluated on all instances)."), booktabs = TRUE, include.rownames = FALSE)
@

@@

perfs = subset(ldf3$data, TRUE, c("instance_id", ldf3$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(0,1)) +
    ylab("fraction of instances solved") + xlab("time [ms]") +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='sans', base_size = 12) +
    theme(legend.justification=c(1,0), legend.position=c(1,0.1), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))
@

@@

<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
# presolver
ldf2 = ldf3
presolvetime = 50
ldf2$data = subset(ldf3$data, ldf3$data$vf2 > presolvetime)
ldf2$best = subset(ldf3$best, ldf3$data$vf2 > presolvetime)
ldf2$train = NULL
ldf2$test = NULL
ldf2 = cvFolds(ldf2)
timesss = subset(timess, timess$instance %in% ldf2$data$instance_id)
ldf2$data$family = factor(timesss[order(timesss$instance, as.character(ldf2$data$instance_id)), 'family'])
ldf2$extra = "family"

@@

tabs = by(ldf2$data, ldf2$data$family, function(x) as.data.frame.matrix(t(sapply(x[,ldf2$performance], mean))))
tab = rbind.fill(tabs)
tab$family = rownames(tab)
tab = tab[,order(names(tab))]
print(xtable(tab, digits = 0, caption = "Mean performance by family."), booktabs = TRUE, include.rownames = FALSE)

@@

tabs = by(ldf2$data, ldf2$data$family, function(x) as.data.frame.matrix(t(sapply(x[,ldf2$performance], median))))
tab = rbind.fill(tabs)
tab$family = rownames(tab)
tab = tab[,order(names(tab))]
print(xtable(tab, digits = 0, caption = "Median performance by family."), booktabs = TRUE, include.rownames = FALSE)

@@

tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
print(xtable(tab, digits = 0, caption = "Preliminary algorithm selection results with presolver."), booktabs = TRUE, include.rownames = FALSE)
@

@@

tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
print(xtable(tab, digits = 0, caption = "Preliminary algorithm selection results with presolver (evaluated on all instances)."), booktabs = TRUE, include.rownames = FALSE)
@

@@

perfs = subset(ldf2$data, TRUE, c("instance_id", ldf2$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(0,1)) +
    ylab("fraction of instances solved") + xlab("time [ms]") +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='sans', base_size = 12) +
    theme(legend.justification=c(1,0), legend.position=c(1,0.1), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))
@

@@

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(0,1)) +
    ylab("fraction of instances solved") + xlab("time [ms]") +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='sans', base_size = 12) +
    theme(legend.justification=c(1,0), legend.position=c(1,0.1), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))
@

\subsection*{Only Glasgow variants}

<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
ldf.glasgow = ldf2
ldf.glasgow$performance = c("glasgow1", "glasgow2", "glasgow3", "glasgow4")
ldf.glasgow$success = c("glasgow1_success", "glasgow2_success", "glasgow3_success", "glasgow4_success")

pnames = ldf.glasgow$performance
snames = ldf.glasgow$success
optfun = min
best = apply(ldf.glasgow$data, 1,
    function(x) {
        tosel = pnames
        nosuccs = sapply(snames[which(as.logical(x[snames]) == FALSE)], function(y) { unlist(strsplit(y, "_"))[1] })
        tosel = setdiff(pnames, nosuccs)
        if(length(tosel) == 0) {
            # nothing was able to solve this instance
            return(NA)
        } else {
            perfs = as.numeric(x[tosel])
            return(tosel[which(perfs == optfun(perfs))])
        }
    })
# simplify...
names(best) = NULL
ldf.glasgow$best = best

resvbs = data.frame(model = "virtual best",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf.glasgow, vbs)),
    solved = sum(successes(ldf.glasgow, vbs)),
    mean.performance = mean(parscores(ldf.glasgow, vbs, factor = 1)),
    median.performance = median(parscores(ldf.glasgow, vbs, factor = 1)))
ressb = data.frame(model = "single best",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf.glasgow, singleBest)),
    solved = sum(successes(ldf.glasgow, singleBest)),
    mean.performance = mean(parscores(ldf.glasgow, singleBest, factor = 1)),
    median.performance = median(parscores(ldf.glasgow, singleBest, factor = 1)))

modelc = classify(rflearner, ldf.glasgow)
resc = data.frame(model = "classification",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf.glasgow, modelc)),
    solved = sum(successes(ldf.glasgow, modelc)),
    mean.performance = mean(parscores(ldf.glasgow, modelc, factor = 1)),
    median.performance = median(parscores(ldf.glasgow, modelc, factor = 1)))
times = sapply(modelc$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classification."), booktabs = TRUE)

modelr = regression(makeLearner("regr.randomForest"), ldf.glasgow)
resr = data.frame(model = "regression",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf.glasgow, modelr)),
    solved = sum(successes(ldf.glasgow, modelr)),
    mean.performance = mean(parscores(ldf.glasgow, modelr, factor = 1)),
    median.performance = median(parscores(ldf.glasgow, modelr, factor = 1)))
times = sapply(modelr$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regression."), booktabs = TRUE)

modelcp = classifyPairs(rflearner, ldf.glasgow)
rescp = data.frame(model = "classifyPairs",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf.glasgow, modelcp)),
    solved = sum(successes(ldf.glasgow, modelcp)),
    mean.performance = mean(parscores(ldf.glasgow, modelcp, factor = 1)),
    median.performance = median(parscores(ldf.glasgow, modelcp, factor = 1)))
times = sapply(modelcp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classificationPairs."), booktabs = TRUE)

modelrp = regressionPairs(makeLearner("regr.randomForest"), ldf.glasgow)
resrp = data.frame(model = "regressionPairs",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf.glasgow, modelrp)),
    solved = sum(successes(ldf.glasgow, modelrp)),
    mean.performance = mean(parscores(ldf.glasgow, modelrp, factor = 1)),
    median.performance = median(parscores(ldf.glasgow, modelrp, factor = 1)))
times = sapply(modelrp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regressionPairs."), booktabs = TRUE)

tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
print(xtable(tab, digits = 0, caption = "Preliminary algorithm selection results with presolver for Glasgow solvers."), booktabs = TRUE, include.rownames = FALSE)
@

<<echo=FALSE,fig.cap='ECDF for algorithms and portfolio (best model).'>>=
vbs.agg = aggregate(as.formula(paste("score~", paste(c("instance_id", "iteration"), sep="+", collapse="+"))), vbs(ldf.glasgow), function(ss) { ss[1] })
vbs.agg$virtual.best = parscores(ldf.glasgow, vbs, factor = 1)
vbs.agg$iteration = NULL
vbs.agg$score = NULL

pmod = data.frame(instance_id = unique(mod$predictions$instance_id), portfolio = parscores(ldf.glasgow, mod, factor = 1))

perfs = subset(ldf.glasgow$data, TRUE, c("instance_id", ldf.glasgow$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(0,1)) +
    ylab("fraction of instances solved") + xlab("time [ms]") +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='sans', base_size = 12) +
    theme(legend.justification=c(1,0), legend.position=c(1,0.1), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))
@

pmod = data.frame(instance_id = unique(mod$predictions$instance_id), portfolio = parscores(ldf.glasgow, mod, factor = 1))
pmod = rbind(pmod, data.frame(instance_id = factor(presolved), portfolio = subset(ldf$data, ldf$data$instance_id %in% presolved)$lad_features))
vf2pre = setdiff(ldf3$data$instance_id, ldf.glasgow$data$instance_id)
pmod = rbind(pmod, data.frame(instance_id = factor(vf2pre), portfolio = subset(ldf$data, ldf$data$instance_id %in% vf2pre)$vf2))

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(0,1)) +
    ylab("fraction of instances solved") + xlab("time [ms]") +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='sans', base_size = 12) +
    theme(legend.justification=c(1,0), legend.position=c(1,0.1), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))
@

\section*{Different timeouts}

Consider timeouts $10^2$\ldots$10^8$ (after filtering and presolving).

<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
timeoutExps = 2:8

tab = rbind.fill(lapply(timeoutExps, function(to) {
    ldf.tmp = ldf2
    if(10^to < asscenario$desc$algorithm_cutoff_time) {
        for(p in ldf.tmp$performance) {
            ldf.tmp$data[paste0(p, "_success")] = sapply(ldf.tmp$data[,p], function(x) x <= 10^to)
            ldf.tmp$data[p] = sapply(ldf.tmp$data[,p], function(x) min(x, 10^to))
        }
        pnames = ldf.tmp$performance
        snames = ldf.tmp$success
        optfun = min
        best = apply(ldf.tmp$data, 1,
            function(x) {
                tosel = pnames
                nosuccs = sapply(snames[which(as.logical(x[snames]) == FALSE)], function(y) { unlist(strsplit(y, "_"))[1] })
                tosel = setdiff(pnames, nosuccs)
                if(length(tosel) == 0) {
                    # nothing was able to solve this instance
                    return(NA)
                } else {
                    perfs = as.numeric(x[tosel])
                    return(tosel[which(perfs == optfun(perfs))])
                }
            })
        names(best) = NULL
        ldf.tmp$best = best
    }
    ldf.tmp$train = NULL
    ldf.tmp$test = NULL
    ldf.tmp = cvFolds(ldf.tmp)

    resvbs = data.frame(model = "virtual best",
        mean.misclassification.penalty = mean(misclassificationPenalties(ldf.tmp, vbs)),
        solved = sum(successes(ldf.tmp, vbs)),
        mean.performance = mean(parscores(ldf.tmp, vbs, factor = 1)),
        median.performance = median(parscores(ldf.tmp, vbs, factor = 1)))
    ressb = data.frame(model = "single best",
        mean.misclassification.penalty = mean(misclassificationPenalties(ldf.tmp, singleBest)),
        solved = sum(successes(ldf.tmp, singleBest)),
        mean.performance = mean(parscores(ldf.tmp, singleBest, factor = 1)),
        median.performance = median(parscores(ldf.tmp, singleBest, factor = 1)))

    modelc = classify(rflearner, ldf.tmp)
    resc = data.frame(model = "classification",
        mean.misclassification.penalty = mean(misclassificationPenalties(ldf.tmp, modelc)),
        solved = sum(successes(ldf.tmp, modelc)),
        mean.performance = mean(parscores(ldf.tmp, modelc, factor = 1)),
        median.performance = median(parscores(ldf.tmp, modelc, factor = 1)))

    modelr = regression(makeLearner("regr.randomForest"), ldf.tmp)
    resr = data.frame(model = "regression",
        mean.misclassification.penalty = mean(misclassificationPenalties(ldf.tmp, modelr)),
        solved = sum(successes(ldf.tmp, modelr)),
        mean.performance = mean(parscores(ldf.tmp, modelr, factor = 1)),
        median.performance = median(parscores(ldf.tmp, modelr, factor = 1)))

    modelcp = classifyPairs(rflearner, ldf.tmp)
    rescp = data.frame(model = "classifyPairs",
        mean.misclassification.penalty = mean(misclassificationPenalties(ldf.tmp, modelcp)),
        solved = sum(successes(ldf.tmp, modelcp)),
        mean.performance = mean(parscores(ldf.tmp, modelcp, factor = 1)),
        median.performance = median(parscores(ldf.tmp, modelcp, factor = 1)))

    modelrp = regressionPairs(makeLearner("regr.randomForest"), ldf.tmp)
    resrp = data.frame(model = "regressionPairs",
        mean.misclassification.penalty = mean(misclassificationPenalties(ldf.tmp, modelrp)),
        solved = sum(successes(ldf.tmp, modelrp)),
        mean.performance = mean(parscores(ldf.tmp, modelrp, factor = 1)),
        median.performance = median(parscores(ldf.tmp, modelrp, factor = 1)))

    sb = levels(singleBest(ldf.tmp)$algorithm)
    cbind(data.frame(timeout = 10^to, single.best = sb), rbind(resvbs, ressb, resc, resr, rescp, resrp))
}))

print(xtable(tab, digits = 0, caption = "Preliminary algorithm selection results for different timeouts with presolver."), booktabs = TRUE, include.rownames = FALSE)
@
